Analysis

### 2022-04-07 analysis/analysis.Rmd
more optical decluttering and improvement

```{r}
pollen_data <- get_download(pollen_locations$neotoma_id)
```

@@

```{r}
res.open_smoothed <- res.open_smoothed[res.open_smoothed$age %in%
seq(from=1000,
    to=10000, by=50),]
ggplot(res.open_smoothed,aes(x=1950-age,y=moving_mean)) + geom_point(aes(color=site), alpha =.5)  + geom_smooth(span = 0.05, color = "black")+ scale_x_continuous(breaks=seq(timeframe[1],timeframe[2],200), limits = timeframe) + labs(y = "Openness score [PCA]",x = "Date",colour = "Sites")  + theme_minimal() + theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

chrono_rough <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "chrono_rough.csv")), row.names = 1)
chrono_vrough <- read.csv(file = normalizePath(file.path(here(), "data","raw_data", "chrono_very_rough.csv")), row.names = 1)
```

@@

```{r}
ggplot() +
  geom_line(data = res.open_final, aes(x = 1950-age, y = scale(mean)), col="darkgreen", alpha = 0.75) +
  geom_line(data = res.sumcal, aes(x = 1950-calBP, y = scale(PrDens)), col="red", alpha = 0.75) +
  geom_line(data = res.aorist, aes(x = date, y = scale(sum)), col="gray", alpha = 0.75) + 
  geom_line(data = res.lss, aes(x = date, y = scale(moving_mean)), col="brown", alpha = 0.75) + scale_colour_manual(values = c("darkgreen", "red", "gray", "brown"), labels = c("Openness Indicator", "Sum Calibration", "Aoristic Sum", "Dendro Dated Settlements"))
```

@@

```{r}
write.csv(all_proxies, file = normalizePath(file.path(here(), "data","preprocessed_data", "all_proxies.csv"), mustWork = F))
```

@@

```{r}
all_proxies <- read.csv(file = normalizePath(file.path(here(), "data","preprocessed_data", "all_proxies.csv")), row.names = 1)
```

@@

# Export common values for the cluster
clusterExport(cl, c("model_code", "model_inits", "model_data", "model_constants", "model_monitors", "batches", "thinning"))

@@

  gc() # Garbage collector for more RAM

@@

MCMCtrace(collector, params = "PopDens", priors = PopDens, pdf = F, ind = T, Rhat = T)
gc()
```

@@

gc()

@@

ggplot(all_proxies_orig) +
  geom_line(aes(x = 1950-age, y = scale(openness), col="Openness Indicator"), alpha = 0.5) +
  geom_line(aes(x = 1950-age, y = scale(sumcal), col="Sum Calibration"), alpha = 0.5) +
  geom_line(aes(x = 1950-age, y = scale(dendro), col="Dendro Dated Settlements"), alpha = 0.5) +
  geom_line(aes(x = 1950-age, y = scale(aoristic_sum), col="Aoristic Sum"), alpha = 0.5) +
  geom_line(data = PopDens_summary, aes(x = rev(1950-all_proxies_orig$age), y=mean, col = "Estimation Result")) + 
  geom_line(data = PopDens_summary, aes(x = rev(1950-all_proxies_orig$age), y=hpdi_l, col = "Estimation Result"), lty=2) + 
  geom_line(data = PopDens_summary, aes(x = rev(1950-all_proxies_orig$age), y=hpdi_u, col = "Estimation Result"), lty=2) + theme_minimal() + 
  scale_colour_manual(values = c("Openness" = "darkgreen", "Sum Calibration" = "red", "Aoristic Sum" = "gray", "Dendro Dated Settlements" = "brown", "Estimation" = "black"), name = "") + theme(legend.position="bottom") + ylab("Scaled values for Proxies,\n P/km² for Estimation") + xlab("cal BCE")
```

>>>>

```{r message=FALSE}
pollen_data <- get_download(pollen_locations$neotoma_id)
```

@@

```{r}
res.open_smoothed <- res.open_smoothed[res.open_smoothed$age %in%
seq(from=1000,
    to=10000, by=50),]
ggplot(res.open_smoothed,aes(x=1950-age,y=moving_mean)) +
  geom_point(aes(color=site), alpha =.5) +
  geom_smooth(span = 0.05, color = "black") +
  scale_x_continuous(breaks=seq(timeframe[1],timeframe[2],200), limits = timeframe) +
  labs(y = "Openness score [PCA]",x = "Date",colour = "Sites") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

@@

chrono_rough <- read.csv(file = normalizePath(
  file.path(here(), "data","raw_data", "chrono_rough.csv")
  ),
  row.names = 1)

chrono_vrough <- read.csv(file = normalizePath(
  file.path(here(), "data","raw_data", "chrono_very_rough.csv")
  ),
  row.names = 1)
```

@@

```{r}
ggplot() +
  geom_line(data = res.open_final, aes(x = 1950-age, y = scale(mean)), col="darkgreen", alpha = 0.75) +
  geom_line(data = res.sumcal, aes(x = 1950-calBP, y = scale(PrDens)), col="red", alpha = 0.75) +
  geom_line(data = res.aorist, aes(x = date, y = scale(sum)), col="gray", alpha = 0.75) + 
  geom_line(data = res.lss, aes(x = date, y = scale(moving_mean)), col="brown", alpha = 0.75) +
  scale_colour_manual(values = c("darkgreen", "red", "gray", "brown"),
                      labels = c("Openness Indicator", "Sum Calibration", "Aoristic Sum", "Dendro Dated Settlements")
                      )
```

@@

```{r}
write.csv(all_proxies, file = normalizePath(
  file.path(here(), "data","preprocessed_data", "all_proxies.csv"
            ),
  mustWork = F)
  )
```

@@

```{r}
all_proxies <- read.csv(file = normalizePath(
  file.path(here(), "data","preprocessed_data", "all_proxies.csv")
  ),
  row.names = 1)
```

@@

# Export common values for the cluster
clusterExport(cl,
              c("model_code",
                "model_inits",
                "model_data",
                "model_constants",
                "model_monitors",
                "batches",
                "thinning"
                )
              )

@@

  gc(verbose=F) # Garbage collector for more RAM

@@

MCMCtrace(collector, params = "PopDens", priors = PopDens, pdf = F, ind = T, Rhat = T)
gc(verbose=F)
```

@@

gc(verbose=F)

@@

ggplot(all_proxies_orig) +
  geom_line(aes(x = 1950-age, y = scale(openness), col="Openness Indicator"), alpha = 0.5) +
  geom_line(aes(x = 1950-age, y = scale(sumcal), col="Sum Calibration"), alpha = 0.5) +
  geom_line(aes(x = 1950-age, y = scale(dendro), col="Dendro Dated Settlements"), alpha = 0.5) +
  geom_line(aes(x = 1950-age, y = scale(aoristic_sum), col="Aoristic Sum"), alpha = 0.5) +
  geom_line(data = PopDens_summary,
            aes(x = rev(1950-all_proxies_orig$age), y=mean, col = "Estimation Result")) + 
  geom_line(data = PopDens_summary,
            aes(x = rev(1950-all_proxies_orig$age), y=hpdi_l, col = "Estimation Result"), lty=2) + 
  geom_line(data = PopDens_summary,
            aes(x = rev(1950-all_proxies_orig$age), y=hpdi_u, col = "Estimation Result"), lty=2) +
  theme_minimal() + 
  scale_colour_manual(
    values = c("Openness" = "darkgreen",
               "Sum Calibration" = "red",
               "Aoristic Sum" = "gray",
               "Dendro Dated Settlements" = "brown",
               "Estimation" = "black"), name = "") +
  theme(legend.position="bottom") +
  ylab("Scaled values for Proxies,\n P/km² for Estimation") +
  xlab("cal BCE")
```
